Regional-scale Base-flow Index of Gauged and Ungauged Basins in Drylands

### 2024-12-03 index.qmd
updating

![Map of Arizona indicating US Geological Survey (USGS) streamgages used in this study. 8-digit HUC subbasin boundaries and physiographic regions shown.](images/StudyArea_20241127.png){#fig-study-area}

@@

![Mean annual BFI for the period of record from instrumented stream flow data.](images/BFI_Instrumented_20241126.png){#fig-instrumented-bfi}

@@

![Trends in BFI over full period of record for instrumented sites used in this study. Red upward (blue downward) arrows indicate an increasing (decreasing) trend at a significance level of 5%. White circles represent sites with no statistically significant trends.](images/BFITrends_20241126.png){#fig-instrumented-trend}

@@

@@

| Classification Group           |  n    |   R2  |  MSE  |  RMSE |  MAE  | NSE            | pbias |
|---------------------------------|------|-------|-------|-------|-------|----------------|-------|
| Climate - Monsoon Dominated     | 3039 | 0.633 | 0.016 | 0.126 | 0.074 | 0.619          | -13.7 |
| Climate - Snowmelt Dominated    | 4685 | 0.733 | 0.015 | 0.121 | 0.087 | 0.725          |  -3.5 |
| PhysRegion - Basin&Range        | 6147 | 0.733 | 0.016 | 0.127 | 0.084 | 0.724          |  -6.3 |
| PhysRegion - CO Plateau         | 1577 | 0.846 | 0.011 | 0.104 | 0.073 | 0.843          |  -3.8 |
| Climate - Warm-Wet              | 1506 | 0.693 | 0.014 | 0.117 | 0.077 | 0.685          |  -8.2 |
| Climate - Warm-Dry              | 2351 | 0.693 | 0.022 | 0.147 | 0.092 | 0.675          | -11.9 |
| Climate - Cool-Wet              | 2350 | 0.738 | 0.011 | 0.106 | 0.078 | 0.736          |  -1.7 |
| Climate - Cool-Dry              | 1517 | 0.831 | 0.012 | 0.111 | 0.078 | 0.827          |  -4.3 |
| Slope - High                    | 3795 | 0.776 | 0.012 | 0.111 | 0.079 | 0.771          |  -3.3 |
| Slope - Low                     | 3929 | 0.724 | 0.018 | 0.133 | 0.085 | 0.713          |  -9.1 |

@@

![Predicted mean annual BFI values for 8-digit HUC (1991-2020)](images/BFI_HUC8_20241126.png){#fig-bfi-huc}

![Predicted mean annual BFI values for all reaches of Strahler stream order 3 and greater](images/BFI_AllStream.pdf){#fig-bfi-streams}

>>>>

![Map of Arizona indicating US Geological Survey (USGS) streamgages used in this study. 8-digit HUC subbasin boundaries and physiographic regions shown.](images/StudyArea_20241203.png){#fig-study-area}

@@

![Mean annual BFI for the period of record from instrumented stream flow data.](images/BFI_Instrumented_20241203.png){#fig-instrumented-bfi}

@@

![Trends in BFI over full period of record for instrumented sites used in this study. Red upward (blue downward) arrows indicate an increasing (decreasing) trend at a significance level of 5%. White circles represent sites with no statistically significant trends.](images/BFITrends_20241203.png){#fig-instrumented-trend}

@@

![Linear relationship between observed BFI and predicted BFI. The solid line is the 1:1 line, the dashed line is regressed to the data.](images/actual-predicted.png){#fig-actual_predicted}

@@

| Classification Group         | n    | R2    | MSE   | RMSE  | MAE   | NSE   | pbias |
|------------------------------|------|-------|-------|-------|-------|-------|-------|
| Climate - Monsoon Dominated  | 3039 | 0.633 | 0.016 | 0.126 | 0.074 | 0.619 | -13.7 |
| Climate - Snowmelt Dominated | 4685 | 0.733 | 0.015 | 0.121 | 0.087 | 0.725 | -3.5  |
| PhysRegion - Basin&Range     | 6147 | 0.733 | 0.016 | 0.127 | 0.084 | 0.724 | -6.3  |
| PhysRegion - CO Plateau      | 1577 | 0.846 | 0.011 | 0.104 | 0.073 | 0.843 | -3.8  |
| Climate - Warm-Wet           | 1506 | 0.693 | 0.014 | 0.117 | 0.077 | 0.685 | -8.2  |
| Climate - Warm-Dry           | 2351 | 0.693 | 0.022 | 0.147 | 0.092 | 0.675 | -11.9 |
| Climate - Cool-Wet           | 2350 | 0.738 | 0.011 | 0.106 | 0.078 | 0.736 | -1.7  |
| Climate - Cool-Dry           | 1517 | 0.831 | 0.012 | 0.111 | 0.078 | 0.827 | -4.3  |
| Slope - High                 | 3795 | 0.776 | 0.012 | 0.111 | 0.079 | 0.771 | -3.3  |
| Slope - Low                  | 3929 | 0.724 | 0.018 | 0.133 | 0.085 | 0.713 | -9.1  |

@@

![Predicted mean annual BFI values for 8-digit HUC (1991-2020)](images/BFI_HUC8_20241203.png){#fig-bfi-huc}

![Predicted mean annual BFI values for all reaches of Strahler stream order 3 and greater](images/BFI_AllStream.png){#fig-bfi-streams}
